A Formal Model of Checked C

### 2023-01-16 sandp23/evaluation.tex
Adding limitations and other eval
Fixing eval

% \review{While I found the idea behind section V very interesting, the current version
%   of this section lacks some details that would help in better understanding (1) 
%   how the approach works, and (2) the overall scope of the approach. 
%   $\\$
%   For instance, the authors state that, following [19], they try to "exercise
%   interesting patterns" by adding "admissible but redundant typing rules" like
%   G-ASTR. There are a few points that are unclear here: (1) are these rules
%   discovered manually or automatically (starting from the Redex semantics)?, (2)
%   are there any guiding principles for coming up with rules that lead to
%   interesting cases?
%   $\\$
%   Later, the authors refer to "generation rules modified to be slightly more
%   permissive" to generate "a little" ill-typed terms. Again, are these rules
%   obtained automatically or defined manually? If the latter, did you follow any
%   methodology to derive such rules? Are these rules the same as the "admissible
%   but redundant typing rules" from above?}
% \liyi{Deena? Leo? }
We evaluate~\systemname in terms of the following three aspects:
\begin{itemize}
\item\textbf{Performance Overhead:} What is the performance overhead (both runtime and memory) in using~\systemname?
\item\textbf{Conversion Effort:} How much developer effort is needed to annotate parts of programs to run in~\systemname?
\item\textbf{Security Impact:} How effective is the isolation provided by~\systemname{} in preventing security vulnerabilities?
\end{itemize}

@@

%\myparagraph{Benchmarking Methodology}
%\systemname is evaluated in terms of performance and conversion efforts similar to that of RLBOX \cite{rlbox-paper} by recording run-time and memory overhead incurred by a \systemname in comparison to an unconverted program in generic-C/checked-C. 
%However, the scope of \systemname changes made on each of the programs is varied and the converted programs themselves are relatively tiny.
%Since each of the program is evaluated on a pre-defined test-suite that runs on a single instance of the program, sandbox creation cost is a one-time constant due to \systemname implementing RLBOX's \cite{rlbox-paper} WebAssembly sandbox API. 
%\liyi{I do not understand the following sentence, what is test-bench? }
%Run-time performance is evaluated with C's~\code{<time.h>} library by placing each of the test-bench calls within the timing scope (Program scope within which the timer runs) and measuring latency delta as a percentage. 
%\liyi{need to rewrite}
%Timing scope excludes marshaling activities within the test-case environment with an intuition that marshaling is irrelevant if tainted-ness of a pointer is propagated from the call site up until its declaration. 
%\liyi{What is Valgrind? }
%Memory overhead is measured with Valgrind's "massif" memory profiler to benchmark the peak memory usage of the Heap. Unlike the Runtime performance, Peak Memory is recorded as a relative offset to original program because most programs are extremely small in comparison to the constant overhead from the sandbox (81 KiB approx). This can further be optimized away by choosing to only compile custom Tainted wrappers for those STDLIB functions that are in use by the tainted pointers in the program. Valgrind's memory figures do not account for Sandbox's Heap allocations which are linearly proportional to sandboxed code and tainted pointers.  
%All of the evaluation was performed using 6-Core Intel i7-10700H with 40 GB of RAM, running Ubuntu 20.04.3 LTS and the benchmarks for every test were sampled as the mean of ten consecutive iterations.
\subsection{Performance Overhead}
Recent work~\cite{jangda2019not} shows that code executed as part of WASM sandbox incurs significant runtime overhead,~\ie$\sim$200\%.
To better understand our runtime overhead, we first perform micro benchmarking of additional sandbox-related operations involved in~\systemname{}.

@@

>>>>

% \review{While I found the idea behind section V very interesting, the current version
%   of this section lacks some details that would help in better understanding (1) 
%   how the approach works, and (2) the overall scope of the approach. 
%   $\\$
%   For instance, the authors state that, following [19], they try to "exercise
%   interesting patterns" by adding "admissible but redundant typing rules" like
%   G-ASTR. There are a few points that are unclear here: (1) are these rules
%   discovered manually or automatically (starting from the Redex semantics)?, (2)
%   are there any guiding principles for coming up with rules that lead to
%   interesting cases?
%   $\\$
%   Later, the authors refer to "generation rules modified to be slightly more
%   permissive" to generate "a little" ill-typed terms. Again, are these rules
%   obtained automatically or defined manually? If the latter, did you follow any
%   methodology to derive such rules? Are these rules the same as the "admissible
%   but redundant typing rules" from above?}
% \liyi{Deena? Leo? }
We evaluate~\systemname in terms of the following three aspects:
\begin{itemize}
\item\textbf{Conversion Effort:} How much developer effort is needed to annotate parts of programs to run in~\systemname?
\item\textbf{Performance Overhead:} What is the performance overhead (both runtime and memory) in using~\systemname?
\item\textbf{Security Impact:} How effective is the isolation provided by~\systemname{} in preventing security vulnerabilities?
\end{itemize}

@@

%\myparagraph{Benchmarking Methodology}
%\systemname is evaluated in terms of performance and conversion efforts similar to that of RLBOX \cite{rlbox-paper} by recording run-time and memory overhead incurred by a \systemname in comparison to an unconverted program in generic-C/checked-C. 
%However, the scope of \systemname changes made on each of the programs is varied and the converted programs themselves are relatively tiny.
%Since each of the program is evaluated on a pre-defined test-suite that runs on a single instance of the program, sandbox creation cost is a one-time constant due to \systemname implementing RLBOX's \cite{rlbox-paper} WebAssembly sandbox API. 
%\liyi{I do not understand the following sentence, what is test-bench? }
%Run-time performance is evaluated with C's~\code{<time.h>} library by placing each of the test-bench calls within the timing scope (Program scope within which the timer runs) and measuring latency delta as a percentage. 
%\liyi{need to rewrite}
%Timing scope excludes marshaling activities within the test-case environment with an intuition that marshaling is irrelevant if tainted-ness of a pointer is propagated from the call site up until its declaration. 
%\liyi{What is Valgrind? }
%Memory overhead is measured with Valgrind's "massif" memory profiler to benchmark the peak memory usage of the Heap. Unlike the Runtime performance, Peak Memory is recorded as a relative offset to original program because most programs are extremely small in comparison to the constant overhead from the sandbox (81 KiB approx). This can further be optimized away by choosing to only compile custom Tainted wrappers for those STDLIB functions that are in use by the tainted pointers in the program. Valgrind's memory figures do not account for Sandbox's Heap allocations which are linearly proportional to sandboxed code and tainted pointers.  
%All of the evaluation was performed using 6-Core Intel i7-10700H with 40 GB of RAM, running Ubuntu 20.04.3 LTS and the benchmarks for every test were sampled as the mean of ten consecutive iterations.

\subsection{Conversion Effort}
The flexibility of~\systemname{} (\sect{subsec:otherusecases}) enables an application to be partitioned in several ways -- with varying levels of overhead and assurance. We explore the following three ways:

\noindent\emph{Checked C and Tainted Partitions ($CTP$):} This is the most comprehensive use case, where the~\cregion partition contains completely annotated Checked C code, and~\ucregion contains one or more tainted functions.
This provides the complete spatial safety of the code in~\cregion{} including isolation from~\ucregion{}.

\noindent\emph{Only Tainted Partition ($TP$):}
This is the general partitioning (\sect{subsec:otherusecases}) use case without Checked C.
This is similar to $CTP$, but~\cregion code does not use any Checked C annotations.
This provides only the isolation guarantee without spatial safety.

\noindent\emph{Only Tainted Pointers ($T_{Pr}$):}
In this use case, we only use tainted pointers, and all code lies in~\cregion.
This is needed for data isolation-only cases, where the developer might want to just isolate certain data (\eg user input) from the rest of the program.
As explained in~\sect{subsec:compilerimple}, all access through tainted pointers will be dynamically checked to ensure that every access is within sandbox.
This provides partial spatial safety by ensuring that any spatial violation involving tainted pointer cannot affect~\cregion.

\input{tables/conversioneffort}
\aravind{Arun, Please fix Table 2 with all details also remove Table 3} 
\subsubsection{Conversion Methodology}
We partitioned each program in our dataset using one of the above three methods.

Our goal is to isolate risky input processing routines from the application code.
We manually analyzed the source code of each application to identify which functions handle the input data and how.
We also looked into previously reported vulnerabilities to identify risky input processing routined.
We picked one of the above methods to partition based on how the input data is processed.
\tbl{} shows the summary of our partitioning of the dataset.
For~\texttt{ProFTPD}, we use $T_{Pr}$ method and mark the input data as trained, and consequently, five other pointers need to be marked as tainted according to the type rules. This resulted in a total of 6 pointer annotations. There is no code in~\ucregion as used $T_{Pr}$ method and used only tainted pointers.
We followed the same approach for~\texttt{LibPNG} (\texttt{png2pnm} and~\texttt{pnm2png}). However, in this case, we had to annotate a lot more pointers (248) because of the complex nature of~\texttt{libPNG}'s internal structures.

For~\texttt{MicroHTTPD} and~\texttt{UFTPD}, we used $TP$ method and marked all of their direct input handled methods as tainted and consequently moved to the sandbox.
We also had to annotate several intermediate pointers as tainted.
For~\texttt{TinyBignum} and~\texttt{Parsons}, we followed $CTP$ and marked all input processing routines as tainted and placed them in the sandbox.
The rest of the non-sandboxed code is annotated completely using~\checkedc types and placed in~\cregion.

\subsubsection{Conversion Effort}
\araivnd{Arun, fix the average hours}
The last column shows the number of hours required to partition each application.
On average, it takes $\sim$ XX hours for each application. However, the exact time depends on the complexity of the code and pointers used in an application.
Although the absolute time is high, partitioning is just a one-time effort for each application.
We start by annotating functions and then iteratively fixing type-checker errors.
Most of the time (80\%) in all applications is spent just running the type-checker.
The type-checker stops at the first error without giving information about all the other variable that needs to be fixed. 
For instance, in the following code:
\begin{minted}[mathescape, escapeinside=||, fontsize=\footnotesize]{c}
_t_Ptr<int> y = ...; 
int *z;
int *x;
|\textcolor{red}{\faRemove}| z = y;
x = z;
\end{minted}
The type-checker displays an error only at the first assignment.
However, to correctly fix it, we need to annotate both~\code{x} and~\code{y}.
If $N$ pointers need to be annotated, then in the worst case, we might have to run the type-checker $N$ times, annotating one additional pointer in every run.
We plan to fix this in our future work and make the type-checker display all the affected pointer variables instead of just the type errors.

\subsection{Performance Overhead}
Recent work~\cite{jangda2019not} shows that code executed as part of WASM sandbox incurs significant runtime overhead,~\ie$\sim$200\%.
To better understand our runtime overhead, we first perform micro benchmarking of additional sandbox-related operations involved in~\systemname{}.

@@

\subsubsection{Overhead on Dataset}
\label{subsec:programoverhead}
